Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
Next steps and gramar edits

There are several limitations and weaknesses that could have affected out research and statistical analysis. First, the variable `numeric_grade` which is the variable that weighs pollster results for accuracy could have been used to determing the how we look at each pollster to make sure the pollster we chose was the most accurate of the most available, and could have included it in our model to increase accuracy of our predictions.Second, as the data from polls change often especially leading up to the election it is difficult to make realtime adjustments as new data becomes available. Next, Harris only announced her candidacy at the end of July, we did not have a very large time frame to take into account whenn looking at her polling data, as often presidential candidates begin campaigning much earlier than just a few months before the election. Furthermore, As we only created a Model for Harris and not Trump we had less to compare to, while we believe our results would not have changed significantly it would have been helpful to consider a model based around Donald Trump. Additionally we could have looked at the states recent voting history for their members of congress, both the senate , and the house of representatives, as well as the current political party holding power in the state, i.e. the party that the governer of each state is affiliated with. Lastly, in recent history elections have been rather close whether they were close in electoral votes or in the popular vote, pollster are hesitant to state that one candidate will win over another even if their research and data shows otherwise as they are afraid to lose their credibility for future elections if they turn out to be wrong or if their analysis is different than the actual results.

@@

- use historical data from past elections to identify strong voting patterns 
- generate confidence intervals 
- integrate more context, and more vairables : Future studies could examine how state-level socioeconomic and political factors, such as unemployment rates, healthcare concerns, or local election issues, might influence voter preferences in each swing state. This would add depth to the model and align predictions more closely with real-world factors.

>>>>

There are several limitations and weaknesses that could have affected out research and statistical analysis. First, the variable `numeric_grade` which is the variable that weighs pollster results for accuracy could have been used to determining the how we look at each pollster to make sure the pollster we chose was the most accurate of the most available, and could have included it in our model to increase accuracy of our predictions.Second, as the data from polls change often especially leading up to the election it is difficult to make realtime adjustments as new data becomes available. Next, Harris only announced her candidacy at the end of July, we did not have a very large time frame to take into account whenn looking at her polling data, as often presidential candidates begin campaigning much earlier than just a few months before the election. Furthermore, As we only created a Model for Harris and not Trump we had less to compare to, while we believe our results would not have changed significantly it would have been helpful to consider a model based around Donald Trump. Additionally we could have looked at the states recent voting history for their members of congress, both the senate , and the house of representatives, as well as the current political party holding power in the state, i.e. the party that the governor of each state is affiliated with. Lastly, in recent history elections have been rather close whether they were close in electoral votes or in the popular vote, pollster are hesitant to state that one candidate will win over another even if their research and data shows otherwise as they are afraid to lose their credibility for future elections if they turn out to be wrong or if their analysis is different than the actual results.

@@

As the election is quickly approachin there are not too many things we would be bale to consider for this election, nevertheless there are a few. First, While we did consider the historical voting paterns of each state, we have not done a rigorous analysis with that data, which we would be able to consider when analyzing a the topic in the future. As, poll results are inherently uncertain and are not absolute indicators of who will win the election, we could use confidence intervals in the future to demonstrate this uncertainty. Next, we could could add more variables into our analysis to create a stronger and more accurate model to help us predict the election with a higher degree of assurance. LAstly, we could consider intangibles more heavily in the future, including recent events, both local and worldwide, considering the socioeconomic status of voters and the voting patterns of certain ethnic groups and how the population and demographic has changed since the last election, as well as general sentiment towards the parties and their presidential candidates.

- integrate more context, and more vairables : Future studies could examine how state-level socioeconomic and political factors, such as unemployment rates, healthcare concerns, or local election issues, might influence voter preferences in each swing state. This would add depth to the model and align predictions more closely with real-world factors.
